Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex
added reference for static analysis
more

A note on notation: \texttt{typewriter} font will be used for Marlowe constructs
% SJT and fragments?
while \emph{math} font will be used for mathematical formulas and pseudo-code.
% Have I got this right?

@@

\noindent
The \emph{spread} parameter here loosely represents the difference between
the average prime 
% SJT explain "prime" here.
rate that the lender expects -- the \emph{benchmark yield} -- and
the rate imposed by the driver - the higher the spread, the higher
the resulting interest rate. The multiplier %effectively 
rescales the interest rate value 
% SJT used value here rather than plot: is that OK?
in order to represent the changes to be made converting between different units
of measurement: how many percentage points 
% SJT percentage points of what?
you would get for a USD-to-kilowatt conversion
and so on.

In the context of ACTUS and other event-based frameworks, 
% SJT - need to explain "event-based" in this context.
there is
one more factor influencing interest rates thorough scaling:

@@

\smallskip
% SJT changed ContractTerm to ContractTerms
\noindent 
\begin{equation}
\ident{Applicability} : \ident{ContractType} \times \ident{ContractTerms} \rightarrow \ident{ApplicabilityType}
\end{equation}
\noindent
where applicability could be: \emph{none}, \emph{always}, \emph{nullable}, or \emph{multiple}.

@@

% SJT what language is this written in?
% can we turn it into Haskell? or Java?
\begin{verbatim}
ContractTerms := sample(qcgenerator) 
Contract := generateMarloweContract(ContractTerms) 
ContractWithAssert := appendAssertion(Contract, assertion) 
runStaticAnalysis(ContractWithAssert)
\end{verbatim}

@@

\subsection{Static analysis for verification}
% SJT added this as a separate sub section, as it covers the static analysis work.
% references added.

>>>>

A note on notation: \texttt{typewriter} font will be used for Marlowe constructs
% SJT and fragments?
while \emph{math} font will be used for mathematical formulas and pseudo-code.
% Have I got this right?
% dk14 looks right to me - I didn't know how to highlight Marlowe constructs properly

@@

\noindent
The \emph{spread} parameter here loosely represents the difference between
the average prime 
% SJT explain "prime" here.
% it's standard financial terminology: https://www.investopedia.com/terms/p/primerate.asp
rate that the lender expects -- the \emph{benchmark yield} -- and
the rate imposed by the driver - the higher the spread, the higher
the resulting interest rate. The multiplier %effectively 
rescales the interest rate value 
% SJT used value here rather than plot: is that OK?
% dk14 maybe "curve" would be better
in order to represent the changes to be made converting between different units
of measurement: how many rate percentage points 
% SJT percentage points of what?
% dk14 rate
you would get for a USD-to-kilowatt conversion
and so on.

In the context of ACTUS and simillar frameworks, 
% SJT - need to explain "event-based" in this context.
% dk14. "Event-driven" but it has no relation to scaling, so I'll remove it
there is
one more factor influencing interest rates thorough scaling:

@@

\smallskip
% SJT changed ContractTerm to ContractTerms
% dk14 OK
\noindent 
\begin{equation}
\ident{Applicability} : \ident{ContractType} \times \ident{ContractTerms} \rightarrow \ident{ApplicabilityType}
\end{equation}
\noindent
where applicability could be: \emph{none}, \emph{always}, \emph{nullable}, or \emph{multiple}.

@@

% SJT what language is this written in?
% can we turn it into Haskell? or Java?
% dk14 it's pseudo-code but I'll make it more Haskell-y
\begin{verbatim}
do
let contractTerms = sample(qcgenerator) 
    contract = generateMarloweContract(contractTerms) 
    contractWithAssert = appendAssertion(contract, assertion) 
runStaticAnalysis(contractWithAssert)
\end{verbatim}

@@

\subsection{Static analysis for verification}
% SJT added this as a separate sub section, as it covers the static analysis work.
% references added.
% dk14. Thanks
